He-Man: A domain-specific language for lightweight concurrency

### 2012-03-06 paper/paper.tex
spellcheck

By far the leanest approach is to write an event loop around kernel facilities
for multiplexed, non-blocking I/O, such as \t{select}, \t{poll}, \t{epoll}, or
\t{kquery}. In this model, all blocking occurs at a single call site in the
code. The programmer is responsible for explicitly maintaining per-client state
and invoking the appropriate client on each I/O event.

@@

To test the suitability of our system for more complicated programs
and to demonstrate seperating network logic and application logic, we
built a simple (and bad) HTTP 1.0 server. The network logic is written
in He-Man and request parsing is written in C. The C side is
implemented as a function that takes a buffer and returns whether it
forms a complete HTTP request and, if so, fills a buffer with the
filename to serve. The entire server is 54 lines of He-Man haskell and
27 lines of C. It suffers from a number of major deficiencies, but is
complete enough to benchmark.

>>>>

By far the leanest approach is to write an event loop around kernel facilities
for multiplexed, non-blocking I/O, such as \t{select}, \t{poll}, \t{epoll}, or
\t{kqueue}. In this model, all blocking occurs at a single call site in the
code. The programmer is responsible for explicitly maintaining per-client state
and invoking the appropriate client on each I/O event.

@@

To test the suitability of our system for more complicated programs
and to demonstrate separating network logic and application logic, we
built a simple (and bad) HTTP 1.0 server. The network logic is written
in He-Man and request parsing is written in C. The C side is
implemented as a function that takes a buffer and returns whether it
forms a complete HTTP request and, if so, fills a buffer with the
file name to serve. The entire server is 54 lines of He-Man Haskell and
27 lines of C. It suffers from a number of major deficiencies, but is
complete enough to benchmark.
